UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-15 files/paper/paper.tex
update

Our fully convolutional discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch
normalization is used. This is due to the fact that WGAN-GP penalizes the norm of the discriminator's gradient with
respect to each input individually, which batch normalization would invalidate. The authors of
\cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed,}, which discriminates at the level of
image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature. This provides a metric for high level frequencies,
which is combinied with the low level frequencies from the $L1$ loss.

In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
\cite{kingma2014adam} with learning rate $1e-4$. When considering the GDL, we use $\alpha = 1$. Following WGAN-GP, the discriminator is updated $n$ times for every
update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$. Our implementation was done using the
Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
is about 8 FPS. We find both of these measures acceptable for underwater tasks.

>>>>

Our fully convolutional discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch
normalization is used. This is due to the fact that WGAN-GP penalizes the norm of the discriminator's gradient with
respect to each input individually, which batch normalization would invalidate. The authors of
\cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer}, but we found no significant improvements.
Our discriminator is modeled as a PatchGAN \cite{isola2016image,li2016precomputed}, which discriminates at the level of
image patches. As opposed to a regular discriminator, which outputs a scalar value corresponding to real or fake, our
PatchGAN discriminator outputs a $32 \times 32 \times 1$ feature matrix, which provides a metric for high level
frequencies. %which is combinied with the low level frequencies from the $L1$ loss.

In all of our experiments, we use $\lambda_{1} = 100$, $\lambda_{GP} = 10$, batch size of 32, and the Adam Optimizer
\cite{kingma2014adam} with learning rate $1e-4$. Following WGAN-GP, the discriminator is updated $n$ times for every
update of the generator, where $n = 5$. For UGAN-P, we set $\lambda_{2} = 1.0$ and $\alpha = 1$. Our implementation was done using the
Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at \url{https://github.com/cameronfabbri/Underwater-Color-Correction}}
All networks were trained from scratch on a GTX 1080 for 100 epochs. Inference on the GPU takes on average $ 0.0138s$,
which is about 72 Frames Per Second (FPS). On a CPU (Intel Core i7-5930K), inference takes on average $ 0.1244s$, which
is about 8 FPS. We find both of these measures acceptable for underwater tasks.
